### 2020-06-10 Article.tex
initial check in.

% IEEEAerospace2012.cls requires the following packages: times, rawfonts, oldfont, geometry
\documentclass[twocolumn,letterpaper]{IEEEAerospaceCLS}  % only supports two-column, letterpaper format

% The next line gives some packages you may find useful for your paper--these are not required though.
%\usepackage[]{graphicx,float,latexsym,amssymb,amsfonts,amsmath,amstext,times,psfig}
% NOTE: The .cls file is now compatible with amsmath!!!

\usepackage{float}         % Used to not have figures placed in random locations.
\usepackage[]{graphicx}    % We use this package in this document
\newcommand{\ignore}[1]{}  % {} empty inside = %% comment

\begin{document}
\title{Daily Solar Array Reconfiguration with the SherpaTT Rover Active Suspension System for Long Traverses}

\author{%
Georges L. J. Labrèche\\
Lorem ipsum dolor sit amet\\
Consectetur adipiscing\\
12345 Eiusmod, Tempor\\
Georges.Labreche@gmail.com
\and
Dr. Florian Cordes\\
DFKI Robotics Innovation Center\\
Robert-Hooke-Straße 1\\
28359 Bremen, Germany\\
Florian.Cordes@dfki.de
}

\maketitle

\thispagestyle{plain}
\pagestyle{plain}

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\end{abstract}

\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lorem ipsum dolor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lorem ipsum dolor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Lorem}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\subsection{Lorem}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\subsection{Lorem}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lorem ipsum dolor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Lorem}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\subsection{Ipsum}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\begin{figure}[H]
\centering
\includegraphics[width=3.25in]{Figures/Placeholder.png}\\
\caption{\textbf{Lorem ipsum dolor sit amet}}
\label{Fig1}
\end{figure}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\subsection{Dolor}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lorem ipsum dolor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendices{}              % note there is no {} to put a title. Each appendix has its own title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% For a single appendix, use the \appendix{} keyword and do not use the \section command.

\section{Lorem ipsum dolor}        % first appendix
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtran}
%\bibliography{IEEEabr,MyBibFile}
\begin{thebibliography}{1}

\bibitem{BIB_01}
Lorem ipsum dolor sit amet, consectetur adipiscing elit.

\bibitem{BIB_02}
Lorem ipsum dolor sit amet, consectetur adipiscing elit.

\bibitem{BIB_03}
Lorem ipsum dolor sit amet, consectetur adipiscing elit.

\end{thebibliography}

\end{document}

### 2020-06-10 Instructions.tex
initial check in.

% IEEEAerospace2012.cls requires the following packages: times, rawfonts, oldfont, geometry
\documentclass[twocolumn,letterpaper]{IEEEAerospaceCLS}  % only supports two-column, letterpaper format

% The next line gives some packages you may find useful for your paper--these are not required though.
%\usepackage[]{graphicx,float,latexsym,amssymb,amsfonts,amsmath,amstext,times,psfig}
% NOTE: The .cls file is now compatible with amsmath!!!

\usepackage[]{graphicx}    % We use this package in this document
\newcommand{\ignore}[1]{}  % {} empty inside = %% comment

\begin{document}
\title{An Example of the 2020 IEEE Aerospace Conference Paper Format Using a \LaTeX~Environment}

\author{%
Erica Deionno\\ 
The Aerospace Corporation\\
2310 E. El Segundo Blvd.\\
El Segundo, CA 90245\\
erica.deionno@aero.org
\and 
Jane Smith\\
Department of ECE\\
University of Nowhere\\
Nowhere, ZS 99999\\
jane.smith@nowhere.edu
%%%% IMPORTANT: Use the correct copyright information--IEEE, Crown, or U.S. government. %%%%%
\thanks{\footnotesize 978-1-7281-2734-7/20/$\$31.00$ \copyright2020 IEEE}              % This creates the copyright info that is the correct 2020 data.
%\thanks{{U.S. Government work not protected by U.S. copyright}}         % Use this copyright notice only if you are employed by the U.S. Government.
%\thanks{{978-1-7281-2734-7/20/$\$31.00$ \copyright2020 Crown}}          % Use this copyright notice only if you are employed by a crown government (e.g., Canada, UK, Australia).
%\thanks{{978-1-7281-2734-7/20/$\$31.00$ \copyright2020 European Union}}    % Use this copyright notice is you are employed by the European Union.
}

\maketitle

\thispagestyle{plain}
\pagestyle{plain}

\begin{abstract}
This paper serves as an example for the use of the \LaTeX~class file for the 2020 Aerospace Conference. The \LaTeX~class file for the 2020 conference has been modified from that of prior year conferences in order to fix minor bugs and to conform to new formatting requirements. Within the class file there are some customized commands that are illustrated in this paper. They are: tableofcontents, acknowledgments, thebiography. There are also comments sprinkled throughout the~.tex file to illustrate the usage of the class file. If you have difficulties or errors using this class file, please contact me at the e-mail address in the author's information slot. Some of the content below is filler designed to show you how a properly formatted paper should look. Read the official ``Author's Instructions for the 2020 IEEE Aerospace Conference'' to find the full description of the paper formatting requirements.
\end{abstract}

\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The annual IEEE Aerospace Conference is a venue for engineers and scientists to present their work to one another. Please submit a paper only if you or a coauthor are committed to attend and present it personally.

An IEEE Aerospace Conference paper is comprised of standard parts described in Section 2 of this paper. Section 3 briefly describes the manuscript style and Section 4 the submission deadlines and procedures. Section 5 discusses presentation of papers at the conference. The Best Paper Awards and paper publication are described in Section 6. Section 7 provides a summary.

Proper formatting of your paper as specified in this document contributes to the successful production of these documents. All papers are also published in PDF format on the {\it IEEE Xplore} web-based system, shortly after the conference concludes.

A double-column format is required, although figures, tables, and equations may be full-page width. Specifications are listed for typeface, type size, headings, column separation, margins, and other style parameters.

Where this document is silent on a formatting question, it is because it is not important or is the writer's option. When in doubt make a choice that makes your document most readable. English is the official language of the conference, and the official page size is 8.5 x 11 inches--do not use A4 paper size.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Paper Organization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
IEEE papers consist of a minimum of nine parts.

\subsection{Title}
The title should indicate the subject of the paper as briefly as possible. The maximum length, including spaces, is 100 characters.

\subsection{Author(s)}
Names of all authors, their affiliations, postal addresses, and e-mail addresses should follow the title, centered on the full width of the page. Do not include titles or degrees except for military rank. Multiple authors may be listed two or three across and as deep as needed. Large numbers of authors should be grouped by address.

\subsection{Abstract}
An abstract of 250 to 500 words should concisely describe the work being reported, its methodology, principal results and significance.

\subsection{Table of Contents}
Major headings and their page numbers are listed in the Table of Contents.

\subsection{Introduction}
The introduction provides background information, such as previous work, and describes how the paper is organized.

\subsection{Body}
The body describes the work in detail and discusses its application. The body should be organized into logical sections with headings and subheadings and be illustrated with figures and tables. Subsidiary information can be relegated to footnotes.

\subsection{Conclusions}
Conclusions should clearly state principal results of the work, its significance, limitations, advantages, and applications. Recommendations for further work are also encouraged.

\subsection{References}
List and number all bibliographical references at the end of the paper.

\subsection{Biography}
Provide a short biography for each author, which can include title, fields of expertise, work experience, education, and relevant personal information. Also include a 1.25 inch wide x 1.5 inch high headshot (at 300 dpi) of each author.

\subsection{Additions}
Add appendices and acknowledgments, if appropriate.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Manuscript Style}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Paper Length}
The paper may be 6 to 20 pages in length.

\subsection{Copyright Notice}
A copyright notice must be placed as a footnote on the first page of the paper. Do not number this footnote. Choose an appropriate alternative from the list of four below:
\begin{itemize}
  \item [(1)] For papers in which all authors are employed by the US government, the copyright notice is: \textbf {U.S. Government work not protected by U.S. copyright} \\
  \item [(2)] For papers in which all authors are employees of a Crown Government (UK, Canada, Australia), the copyright notice is: \\{\bf 978-1-7281-2734-7/20/\$31.00 \copyright2020 Crown}\\
  \item [(3)] For papers in which all authors are employed by the European Union, the copyright notice is: \\{\bf 978-1-7281-2734-7/20/\$31.00 \copyright2020 European Union}\\
  \item [(4)]  For all other papers the copyright notice is: \\{\bf  978-1-7281-2734-7/20/\$31.00 \copyright2020 IEEE}
\end{itemize}

\subsection{Paper, Margins, and Spacing}
Format your electronic submission to 8.5 x 11 inch page size in double-column format with 0.75 inch margins on each side, top and bottom. There should be 0.25 inch between columns, which are justified both right and left.

Lines of text should be single-spaced, except for double spacing before headings and space-and-a-half after.

\subsection{Headers and Footers}
No headers are permitted. Utilize footers only for page numbers, which are centered at the bottom of each page.

\subsection{Headings}
\subsubsection{Major Headings}
Centered in the column with a double space before and space-and-a-half after.
\subsubsection{Subheadings}
Italicized and placed flush on the left-hand margin on a separate line. Use a double space before and space-and-a-half after.
\subsubsection{Subsubheadings}
Italicized, followed by an em dash and run in at the beginning of the paragraph. This paragraph has a correctly formatted subsubheading.

\subsection{Other Elements}
\subsubsection{Equations}
Equations should be centered in the column. When numbering an equation, enclose the number in parentheses placed flush with the right-hand margin of the column, as shown in the sample equations that follow.
\begin{equation}
{\bf F}=m{\bf a}
\end{equation}
\begin{equation}
e=mc^2
\end{equation}

Mathematical derivations and proofs should be developed in appendices.

\subsubsection{Figures}
Place figures as close to the text reference as possible. Center figure titles directly below the figure, as shown in Figure 1.

Figures should be sized for easy reading. No lettering in a figure should be smaller than 10 points. Scan photographs at a 300-dpi resolution and embed them in the paper. High-resolution images should be reduced to 300 dpi at the size they will be printed.

\begin{figure*}
\centering
\includegraphics[width=4in]{Placeholder.eps}
\caption{\bf{Here is an example of a figure that spans both columns.}}
\label{FlowChart}
\end{figure*}

\subsubsection{Tables}
Place tables as close to the text reference as possible. Use the full width of the page for legibility, if required. Center table titles directly {\bf above} the table.

\subsubsection{Footnotes}
All footnotes\footnote{\bf This is an example of a footnote.} following the IEEE copyright notice are numbered consecutively.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Paper Submission}
Submission due dates and deadlines are given in Table \ref{DueDates}.

\begin{table}
\renewcommand{\arraystretch}{1.3}
\caption{\bf Summary of Due Dates}
\label{DueDates}
\centering
\begin{tabular}{|c|c|}
\hline
\bfseries Event & \bfseries Due Date \\
\hline\hline
Abstracts Due               & July 1, 2019 \\
Review Paper Deadline & October 18, 2019 \\
Final Revised Paper Deadline          & January 8, 2020\\
IEEE Copyright Form Due     & January 8, 2020\\
\hline
\end{tabular}
\end{table}

\subsection{Abstract}
An abstract of 250 to 500 words describing the planned content of the paper must be submitted electronically at the conference website.

\subsection{Review Paper}
The paper submitted for review must be a complete, fully formatted, and proofread manuscript, ready for publication. NO paper submitted for review after the deadline will be reviewed or admitted to the conference.

\subsection{Final Paper}
Following receipt of review comments, make appropriate revisions to the paper and submit a final version for publication.

\subsection{IEEE copyright Form}
An IEEE Copyright Release Form for each paper, signed by the author or author's employer, is due with the final paper.

Copyright forms are available at the conference website and can be submitted electronically at the IEEE site linked for this purpose or by mail to the address provided on the website.

\subsection{ITAR Compliance}
International Traffic in Arms Regulation (ITAR) controls the export and import of defense articles and defense services as detailed in the U.S. Munitions List \cite{ITAR}.

Authors who are U.S. nationals (including green card holders), work for a U.S.-based organization regardless of where they are physically located, or work at a U.S. location of a non-U.S.-based organization, must ensure that ITAR compliance has been obtained for any and all papers submitted to IEEE for publication.

\subsection{Organizational Approval}
Authors are expected to obtain any needed clearances for their work to be freely published by the IEEE. Submission of your paper implies that it has received the proper clearances from your company, affiliation, or organization.

\subsection{Submission to the \underline{www.aeroconf.org} website}
Before Submitting your abstract or paper:
\begin{itemize}
  \item [1)] Scan your document with a current anti-virus product. (If a virus is detected, your file willl be deleted) \\
  \item [2)] Remove passwords or other protection from your file that would prevent it from being opened. \\
  \item [3)] Submit a PDF version of your abstract of paper via the website.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Presentation at the Conference}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Prepare a presentation to be delivered at the conference, using Microsoft PowerPoint or similar software, that summarizes the major concepts of your paper.

\subsection{Allotted Time}
Time allotted for presentations is 18 minutes, with an additional 5 minutes for questions. The time limit will be strictly enforced.

\subsection{Projection}
A projector and screen will be set up in each meeting room. Bring your slide set on a laptop to plug in to the projector. Also bring a copy of your presentation on a USB drive, in case your session chair chooses to consolidate all the presentations on a single laptop before the session starts.

\subsection{Presentation}
Tips on giving the presentation will be sent to registered authors in advance of the conference.

\subsection{Special Displays}
Displays of hardware or software an author believes to be of wide interest to conference attendees may be set up with permission of the Technical Program Committee and by special arrangement with the Conference Manager.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Best Paper Award and Publication}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Best Paper Award}
Awards for Best Paper Award in each track and the overall conference are given each year for excellence in technical innovation and exposition in the written paper. The selection is conducted prior to the conference and the award is presented at the conference.

\subsection{Publication}
Papers presented at the IEEE Aerospace Conference are published in two forms:
\begin{itemize}
  \item [1)] On an online database accessible by registrants \\
  \item [2)] In the official Conference Proceedings on the web-based {\it{IEEE Xplore}} System following the conference
\end{itemize}

\begin{figure}\label{OneColumn}
\centering
\includegraphics[width=3.25in]{placeholder.eps}\\
\caption{\textbf{ A single column figure.}}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This Author's Instructions document serves as a template for papers prepared for the 2020 IEEE Aerospace Conference. All paper submissions are accomplished online, through the IEEE Aerospace Conference website at \underline {www.aeroconf.org} \cite{AeroConf}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendices{}              % note there is no {} to put a title. Each appendix has its own title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% For a single appendix, use the \appendix{} keyword and do not use the \section command.

\section{More Information}        % first appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%
This is the first appendix.

\subsection{Comments}
If you have only one appendix, use the ``appendix'' keyword.

\subsection{More Comments}
Use section and subsection keywords as usual.

\section{Yet More Information}    % second appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This is the second appendix.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments
Project sponsors may be acknowledged in this section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtran}
%\bibliography{IEEEabr,MyBibFile}
\begin{thebibliography}{1}

\bibitem{ITAR}
U.S. Munitions List, Sections 38 and 47(7) of the Arms Export Control Act (22 U.S.C 2778 and 2794(7).

\bibitem{AeroConf}
Aerospace Conference Web site: \underline{www.aeroconf.org}.

\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\thebiography
%% This biostyle allows you to insert your photo size 1in X 1.25in
\begin{biographywithpic}
{Erica DeIonno}{DeIonno.eps}
received her B.S./M.S. and Ph.D. degrees in chemistry from UCLA. She currently works in the Innovation Office at The Aerospace Corporation and is responsible for selected internal research programs, university collaborations, and technical communications. Before her current role, she spent 10 years in the Physical Sciences Laboratories. Her work included radiation testing and modeling of emerging resistive RAM technologies and space degradation modeling and lifetime predictions of solar cells and arrays.
\end{biographywithpic}

\begin{biographywithpic}
{Jane Smith}{blankpic.eps}
received her B.S. degree in Electrical Engineering in 1985 and a Ph.D. in Aerospacel Engineering from the Massachusettes Institute of Technology in 1990. She is currently a professor of Aerospace Engineering at the University of Nowhere. Her interests include secure communications and space exploration.

\end{biographywithpic}

\end{document}

### 2020-06-10 make.sh

@@ -1,0 +1,2 @@
+#!/bin/bash
+pdflatex Article.tex

### 2020-06-12 Article.tex
First draft of the paper.

@@
 
-\usepackage{float}         % Used to not have figures placed in random locations.
-\usepackage[]{graphicx}    % We use this package in this document
-\newcommand{\ignore}[1]{}  % {} empty inside = %% comment
+\usepackage{siunitx}      % Use for scientific notation.
+\usepackage{float}        % Use to not have figures placed in random locations.
+\usepackage[]{graphicx}   % We use this package in this document.
+\usepackage[font=footnotesize,labelfont=bf,textfont=bf]{caption}
+\usepackage{subcaption}   % neue subfigure-Umgebung %% should probably not be used with memoir: generates warning
+\usepackage[nolist,nohyperlinks]{acronym} % Use this for acronyms, unlisted.
+
+% New commands.
+\newcommand{\ignore}[1]{}                  % {} empty inside = %% comment.
+\newcommand{\refFig}[1]{{Figure}~\ref{#1}} % Command for figure reference.
+\newcommand{\refTab}[1]{{Table}~\ref{#1}}  % Command for table reference.
+
+% Renew commands.
+\renewcommand\thefootnote{{(\alph{footnote})}} % footnote formatting and colors
+
+% Define common figure sizes for subfigures -> redefined in each environment
+\newlength{\subfigureWidth}
+\setlength{\subfigureWidth}{0.24\textwidth}
+\newlength{\graphicsHeight}
+\setlength{\graphicsHeight}{25mm}
+
+\begin{acronym}
+  \acro{DFKI}{German Research Center for Artificial Intelligence}
+  \acro{EOL}{End of Life}
+  \acro{IL}{InnerLeg}
+  \acro{MRS}{Multi-Robot System}
+  \acro{OL}{OuterLeg}
+  \acro{PLI}{Payload Item}
+  \acro{RA}{Robotic Arm}
+  \acro{RIC}{Robotics Innovation Center}
+  \acro{SA}{Solar Array}
+  %\acrodefplural{SA}[SAs]{Solar Arrays}
+  \acro{TRL}{Technology Readiness Level}
+  \acro{WD}{WheelDrive}
+  \acro{WS}{WheelSteering}
+\end{acronym}
 
 \begin{document}
-\title{Daily Solar Array Reconfiguration with the SherpaTT Rover Active Suspension System for Long Traverses}
+\title{Using a Rover's Active Suspension System as a 2-Axis Solar Tracker Mechanism}
 
+% Alternative titles:
+%   1. Daily Solar Array Reconfiguration with the SherpaTT Rover Active Suspension System for Long Traverses
+%   2. Extending Rover Traverse Coverage with the SherpaTT Active Suspension System for Daily Solar Array Reconfiguration
+%   3. Using the SherpaTT Active Suspension for Daily Optimization of Solar Array Configuration
+%   4. The SherpaTT Rover's Active Suspension System as a Mechanism for Daily Optimization of Solar Array Configuration
+%   5. Using the SherpaTT Active Suspension System for Daily Optimization of Rover Solar Array Configuration
+%   6. The SherpaTT Rover Active Suspension System as a Mechanism for Daily Solar Array Optimization
+%   7. Mars Traverse Distance Gains Using a Rover's Active Suspension System as a 2-Axis Solar Tracker Mechanism
 \author{%
@@
 \begin{abstract}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+The SherpaTT rover is prepared for further autonomous long distance traverses in terrain akin to the Martian environment.
+However, it features a fueled power generator which cannot be employed in extra-terrestial scenarios.
+As the rover is meant to approach a higher technology readiness level, a photovoltaic power subsystem is proposed to guide future design iterations.
+This paper presents the solar array sizing, design, and integration processes considered for two Martian mission sites: Iani Chaos at \SI{2}{\degree}S and Ismenius Cavus at \SI{34}{\degree}N.
+An alternative use case for the active suspension system is presented so that the proposed solar arrays may be inclined and oriented into power generating configurations that are more favorable than those achieved with passive suspension rovers.
+This results in traverse gains of up to \SI{34}{\percent} and \SI{25}{\percent} for clear days at Iani Chaos and Ismenius Cavus, respectively.
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+The exploration rover SherpaTT has a total mass of approximately \SI{160}{\kilo\gram} and the legs as well as the \ac{RA} weigh about \SI{25}{\kilo\gram} each.
+The wheeled-leg active suspension system allows the rover to assume different poses with varying inertial moments.
+The rover is one of many systems comprising a \ac{MRS} developed at the \ac{DFKI}'s \ac{RIC}.
+
+The rover has undergone several field trial campaigns, particularly with a Mars analogue terrain field deployment in Utah, USA, where a logistics chain for sample return was evaluated.
+The rover's versatility has been demonstrated through a multitude of tasks such as assembling surface deployable payloads and using its \ac{RA} for soil sampling with modular \ac{PLI} sampling devices \cite{Cordes2018b}.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=2.9in]{figures/images/sherpatt-actively-articulated-suspension-sytem.png}\\
+  \caption{Description of DoF present in SherpaTT’s
+suspension system and placement of force-torque sensor}
+  \label{fig:sherpatt-actively-articulated-suspension-system}
+\end{figure}
+
+The actively articulated suspension system consists of four wheeled-legs with a total of 20 motors.
+The distribution of motors across a single leg is shown in \refFig{fig:sherpatt-actively-articulated-suspension-system}.
+Each leg is equipped with three suspension motors and two drive motors.
+The suspension motors are responsible for Pan, \ac{IL}, and \ac{OL} revolute joint rotations whereas the drive motors are responsible for \ac{WS} and \ac{WD}.
+
+The rover has been deployed in several field experiments where it was put under test within natural and unstructured Mars analogue terrain with respect to general morphology and geology.
+The rover displayed the ability to cope with natural terrain and to fulfill the task of being an exploration and sampling rover.
+Further development is required on its electrical power subsystem if it is to operate in long term missions.
+This paper explores \ac{SA} configurations for the a Mars environment in order to guide future design iterations to navigate the topography of this planetary surface.
+The constraints imposed from the active suspension system with flexible footprints and varying heights of structural parts of the legs are considered in the design phase.
+
+Initial \ac{SA} sizing requirements are derived from Mars mission sites, Iani Chaos and Ismenius Cavus, that impose energy storage and consumption constraints based on available daily insolations.
+The design is driven by the use the rover's active suspension system as a 2-axis solar tracking mechanism, enabling daily reconfiguration of the \ac{SA} surface inclination and orientation angles.
+An alternative use of the wheeled leg system is thus presented for a use case that goes beyond the scenario of negotiating complex terrains such as steep slopes.
+Specifically, the findings demonstrate traverse and mass reductions gains that are obtained with a suspension system driven inclination and orientation capable \ac{SA} surface when compared to a horizontal configuration.
+
+Past research on active suspension systems are restricted to analyzing benefits with respect to traversing challenging topographies.
+Studying how this system can be used for other mission planning elements broadens the field of research.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Lorem ipsum dolor}
+\section{Power Budget}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Large inclination angles are typically preferred with respect to increased insolation for a sun-facing surface.
+However, constraints on the rover's active suspension system imposes a limit on the achievable body pitch angle.
+Body pitch commands of up to \SI{10}{\degree} are experimentally evaluated during steep slope climbing in \cite{Cordes2018a}.
+Modeling higher pitch angles resulted in poor wheel-ground contact angle due to the \ac{WS} axis having the same tilt as the rover's body.
+The attainable tilt is thus restricted resulting in a maximum \ac{SA} surface inclination angle of $\beta = \SI{10}{\degree}$.
+
+\input{tables/insolation-iani-chaos-clear-and-dusty-days.tex}
+
+\refTab{tab:insolation-iani-chaos-clear-and-dusty-days} and \refTab{tab:insolation-ismenius-cavus-clear-and-dusty-days} presents the best and worst case daily insolations $H_{h}$, on horizontal \ac{SA} surface, compared to those obtained with $H_{\beta}$, on an inclined sun-facing \ac{SA} surface.
+Optical depths $\tau$ for clear to dusty days are evaluated with the daily insolations expressed in \si{Wh.m^{-2}} and the gains in percentage.
+The solar insolation values are taken from \cite{Labreche2020}.
+
+\input{tables/insolation-ismenius-cavus-clear-and-dusty-days.tex}
+
+Gains obtained in daily insolation with an inclined surface are more pronounced for sites further away from the equator.
+For a typical optical depth of $\tau = 0.4$, the average daily insolation gain on the inclined surface is approximately \SI{7}{\percent} at Iani Chaos and \SI{9}{\percent} at Ismenius Cavus.
+Due to the mostly diffuse composition of solar irradiance at higher optical depths, inclined surfaces become irrelevant during global dust storms.
+For $\tau \geq 2$, gains in daily insolation become negligible at both sites.
+
+As a prerequisite to \ac{SA} sizing, power budgets are defined for hibernation and flat terrain traverse reference Sols.
+These are presented in \refTab{tab:hibernation-sol-power-budget} and \refTab{tab:worst-case-traverse-sol-power-budget}.
+Hibernation power draws are identical during day and nighttime so the hibernation reference Sol does not have a best or worse case Sol with respect to available sunlight.
+
+\input{tables/power-budget-hibernation-sol.tex}
+
+Durations of daylight dependent modes in the traverse reference Sol are based on the total length of daylight time for worst case daily insolations Sols presented in \refTab{tab:insolation-iani-chaos-clear-and-dusty-days} and \refTab{tab:insolation-ismenius-cavus-clear-and-dusty-days} with $\tau$ factor 1 and $\beta=\SI{10}{\degree}$ for the \ac{SA} surface inclination angle.
+Propulsion power draws for the rover's flat terrain traverse mode is determined from data collected during the SherpaTT Utah field trial.
+
+\input{tables/worst-case-power-budget-flat-traverse-sol-tau-1.tex}
+
+The \textit{Optimal Pose} mode in \refTab{tab:worst-case-traverse-sol-power-budget} consists of using the rover's active suspension system to reconfigure the \ac{SA} surface orientation and inclination so that daily insolation is maximized on the following Sol.
+In this manner, the suspension system undertakes the role of a 2-axis solar tracking mechanism.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Lorem ipsum dolor}
+\section{Solar Array Sizing}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Lorem}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 
-\subsection{Lorem}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+The solar cell coverage area $A$ is expressed as:
 
-\subsection{Lorem}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\begin{equation}
+  \label{eq:solar_cell_coverage_area}
+  A = \frac{E}{\eta \cdot H \cdot PR}
+\end{equation}
+
+where $E$ is the rover's energy requirement, $\eta$ is the solar cell efficiency, $H$ is the daily insolation, and $PR$ is the solar cell performance ratio.
+An initial \ac{SA} sizing is determined with $H_{\beta}$ from \refTab{tab:insolation-iani-chaos-clear-and-dusty-days} and \refTab{tab:insolation-ismenius-cavus-clear-and-dusty-days} as well as $E$ from \refTab{tab:worst-case-traverse-sol-power-budget} for the worst case daily insolation at $\tau$ factor 1.
+\ac{EOL} values for $PR$ and $\eta$ are determined in \cite{Labreche2020}:
+
+\begin{itemize}
+  \item [(1)] $H$\,$=$\,\SI{2479}{Wh.m^{-2}} and $E$\,$=$\,\SI{775}{\watt\hour} at Iani Chaos.
+  \item [(2)] $H$\,$=$\,\SI{1345}{Wh.m^{-2}} and $E$\,$=$\,\SI{750}{\watt\hour} at Ismenius Cavus.
+  \item [(3)] $PR_{EOL}$\,$=$\,0.62.
+  \item [(4)] $\eta_{EOL}$\,$=$\,0.22.
+\end{itemize}
+
+Furthermore, the solar cell packing efficiency is assumed at \SI{85}{\percent}, the \ac{SA} surface density at \SI{3.7}{kg.m^{-2}}, and the average slippage at \SI{15}{\percent} when traversing a flat terrains for any given distance.
+Traversing is constrained to daylight hours and it is assumed that on average traversing only occurs every third Sol.
+
+At Iani Chaos, the required \ac{SA} area is \SI{2.7}{m^{2}} and the mass 9.95 \si{\kilo\gram}.
+\ac{SA} surface inclination of \SI{10}{\degree} with a daily sun-facing reorientation results in a \ac{SA} size decrease of \SI{3.9}{\percent} when compared against a horizontal surface configuration.
+The maximum flat traverse distance achievable over the course of a Martian year is increased by \SI{13.22}{\percent} from \SI{42.43}{\kilo\meter} to \SI{48.04}{\kilo\meter} with $\tau$ factor 1 during global dust storm season and 0.4 otherwise.
+At Ismenius Cavus, the required \ac{SA} area is \SI{4.8}{m^{2}}, its mass 17.8 \si{\kilo\gram}, and a \SI{4.6}{\percent} \ac{SA} size decrease is achieved.
+The maximum flat traverse distance achievable over the course of a Martian year is increased by \SI{2.13}{\percent} from \SI{63.05}{\kilo\meter} to \SI{64.39}{\kilo\meter}.
+
+The traverse distance gains attributed to \ac{SA} inclination capabilities do not justify taking advantage of the rover's active suspension system for the purpose of increasing solar power generation.
+This is particularly true at Ismenius Cavus.
+The savings in \ac{SA} size and mass also leave much to be desired.
+Furthermore, the large \ac{SA} are problematic in terms of rover integration.
+This is illustrated in \refFig{fig:sa-area-initial-sizes}.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=3.25in]{figures/images/sa-area-initial-sizes.png}\\
+  \caption{Initial \ac{SA} sizing. The outlined square areas are equivalent to \ac{SA} areas of \SI{2.7}{m^{2}} for Iani Chaos and \SI{4.8}{m^{2}} for Ismenius Cavus.}
+  \label{fig:sa-area-initial-sizes}
+\end{figure}
+
+To explain the lack of significant gains, the generated \ac{SA} energy and maximum traverse durations is plotted in \refFig{fig:plot:ismenius-cavus-generated-energy-and-max-traverse-durations} for Ismenius Cavus.
+During clear days at $\tau$ factor 0.4, a ceiling is imposed on the daily maximum traverse durations due to the available daylight time for traversing.
+The maximum traverse time is already attained with a horizontal \ac{SA}, making an inclined \ac{SA} irrelevant in terms traverse distance gains.
+As seen in \refFig{fig:plot:sub:ismenius-cavus-max-traverse-durations}, the inclined \ac{SA} is only slightly advantageous during the global dust storm season with a $\tau$ factor of 1.
+
+\begin{figure}[h]
+\captionsetup[subfigure]{justification=centering}
+  \centering
+  \setlength{\subfigureWidth}{0.24\textwidth}
+  \setlength{\graphicsHeight}{40mm}
+  \begin{subfigure}[t]{\subfigureWidth}
+    \centering
+    \includegraphics[height=\graphicsHeight]{figures/plots/ismeniuscavus-daily-generated-energy-for-solar-cell-coverage-area-41m2.png}
+    \subcaption{Generated Energy}
+    \label{fig:plot:sub:ismenius-cavus-generated-energy}
+  \end{subfigure}\hfill
+  \begin{subfigure}[t]{\subfigureWidth}
+    \centering
+    \includegraphics[height=\graphicsHeight]{figures/plots/ismeniuscavus-75w-max-traverse-durations-for-solar-cell-coverage-area-41m2.png}
+    \subcaption{Maximum Traverse Durations}
+    \label{fig:plot:sub:ismenius-cavus-max-traverse-durations}
+  \end{subfigure}\\[0.8ex]
+  \caption{Generated energy and maximum flat terrain traverse duration at Ismenius Cavus with solar cell coverage area of \SI{4.1}{m^{2}}.
+Surface inclination angle $\beta$ is \SI{10}{\degree}.
+$\tau$ factor 1 is used for global dust storm season ($\SI{185}{\degree} \leq L_{s} \leq \SI{315}{\degree}$) and 0.4 otherwise.
+The \textit{available daylight traverse time} corresponds to the amount of daylight hours left in a \textit{Traverse Sol} after subtracting the time taken by rover modes unrelated to traversing.}
+  \label{fig:plot:ismenius-cavus-generated-energy-and-max-traverse-durations}
+\end{figure}
+
+However, no such ceiling can be observed for Iani Chaos in \refFig{fig:plot:iani-chaos-generated-energy-and-max-traverse-durations} which would explain the poor gains for that mission site scenario.
+In both cases, lack of traverse distance gains is more closely tied to the $\tau$ factor selected when defining the worst case reference Sol that drives \ac{SA} sizing.
+At high optical opacities, increased light scattering by airborne Martian dust results in $H_{\beta} \approx H_{h}$ due to diffuse insolation being the largest component in the global insolation.
+Thus, when \ac{SA} sizing for power generation during dusty Sols, the resulting inclined \ac{SA} surface yield little to no benefits over horizontal surfaces with respect to traverse distance gains as well as \ac{SA} mass and area.
+
+\begin{figure}[h]
+\captionsetup[subfigure]{justification=centering}
+  \centering
+  \setlength{\subfigureWidth}{0.24\textwidth}
+  \setlength{\graphicsHeight}{40mm}
+  \begin{subfigure}[t]{\subfigureWidth}
+    \centering
+    \includegraphics[height=\graphicsHeight]{figures/plots/ianichaos-daily-generated-energy-for-solar-cell-coverage-area-23m2.png}
+    \subcaption{Generated Energy}
+    \label{fig:plot:sub:iani-chaos-generated-energy}
+  \end{subfigure}\hfill
+  \begin{subfigure}[t]{\subfigureWidth}
+    \centering
+    \includegraphics[height=\graphicsHeight]{figures/plots/ianichaos-75w-max-traverse-durations-for-solar-cell-coverage-area-23m2.png}
+    \subcaption{Maximum Traverse Durations}
+    \label{fig:plot:sub:iani-chaos-max-traverse-durations}
+  \end{subfigure}\\[0.8ex]
+  \caption{Generated energy and maximum flat terrain traverse duration at Iani Chaos with solar cell coverage area of \SI{2.3}{m^{2}}.
+The same considerations were taken as in \refFig{fig:plot:ismenius-cavus-generated-energy-and-max-traverse-durations}.}
+  \label{fig:plot:iani-chaos-generated-energy-and-max-traverse-durations}
+\end{figure}
+
+To resolve this, the worst case power budget in \refTab{tab:worst-case-traverse-sol-power-budget} is set aside and the \ac{SA} sizing process is approached inversely by identifying solar cell coverage area targets based on the traverse distance gains brought about by an inclined surface.
+\refFig{fig:plot:flat-traverse-gains-for-different-sa-area} compares the traverse distance gains obtained with an inclined \ac{SA} surface for different solar cell coverage areas and optical depths.
+
+\begin{figure}[h]
+\captionsetup[subfigure]{justification=centering}
+  \centering
+  \setlength{\subfigureWidth}{0.24\textwidth}
+  \setlength{\graphicsHeight}{40mm}
+    \begin{subfigure}[t]{\subfigureWidth}
+      \centering
+      \includegraphics[height=\graphicsHeight]{figures/plots/ianichaos-75w-traverse-gains-for-different-solar-cell-coverage-areas.png}
+    \subcaption{Iani Chaos}
+    \label{fig:plot:sub:ismenius-chaos-flat-traverse-gains-for-different-sa-area}
+    \end{subfigure}\hfill
+    \begin{subfigure}[t]{\subfigureWidth}
+      \centering
+      \includegraphics[height=\graphicsHeight]{figures/plots/ismeniuscavus-75w-traverse-gains-for-different-solar-cell-coverage-areas.png}
+    \subcaption{Ismenius Cavus}
+    \label{fig:plot:sub:iani-chaos-flat-traverse-gains-for-different-sa-area}
+    \end{subfigure}\\[0.8ex]
+    \caption{Average flat terrain traverse distance gains at mission sites for different solar cell coverage areas.
+\ac{SA} inclination angle $\beta_{max} = \SI{10}{\degree}$ with orientation angles $\gamma_{c}$ set to their optimal values for the considered traverse Sols.}
+    \label{fig:plot:flat-traverse-gains-for-different-sa-area}
+\end{figure}
+
+Targeting a solar cell coverage area of \SI{1.5}{m^{2}} at Iani Chaos results in an average \SI{34}{\percent} gain in traverse for a clear day at $\tau$ factor 0.4.
+The gain remains significant at \SI{23}{\percent} for a dusty day at $\tau$ factor 1.
+The increase in gain observe for $\tau$ factors greater than 1 are inconsequentially tied to negligible distances.
+At Ismenius cavus, a solar cell coverage area of \SI{2.4}{m^{2}} results in \SI{25}{\percent} and \SI{10}{\percent} gains for $\tau$ factor 0.4 and 1, respectively.
+Applying the same packing efficiency and \ac{SA} surface density as the initial sizing results in \ac{SA} areas of \SI{1.7}{m^{2}} at Iani Chaos with a mass of \SI{6.3}{\kilo\gram} and \SI{2.8}{m^{2}} at Ismenius Cavus with a mass of \SI{10.4}{\kilo\gram}.
+The maximum daily traverse durations attainable at both sites with these target \ac{SA} areas are shown in \refFig{fig:plot:final-maximum-traverse-durations-at-missions-sites}.
+However, these gains come with significantly reduced maximum flat traverse distance coverage of \SI{12}{\kilo\meter} at Iani Chaos and \SI{35}{\kilo\meter} at Ismenius Cavus.
+Mission design with or without \ac{SA} surface inclination thus not only depend on \ac{SA} size and mass constraints but also on mission requirements with respect to target traverse coverages.
+
+\begin{figure}[h]
+\captionsetup[subfigure]{justification=centering}
+  \centering
+  \setlength{\subfigureWidth}{0.24\textwidth}
+  \setlength{\graphicsHeight}{40mm}
+  \begin{subfigure}[t]{\subfigureWidth}
+    \centering
+    \includegraphics[height=\graphicsHeight]{figures/plots/ianichaos-75w-max-traverse-durations-for-solar-cell-coverage-area-15m2.png}
+    \subcaption{Iani Chaos, solar cell coverage = \SI{1.5}{m^{2}}}
+    \label{fig:plot:sub:final-maximum-traverse-durations-iani-chaos}
+  \end{subfigure}\hfill
+  \begin{subfigure}[t]{\subfigureWidth}
+    \centering
+    \includegraphics[height=\graphicsHeight]{figures/plots/ismeniuscavus-75w-max-traverse-durations-for-solar-cell-coverage-area-24m2.png}
+    \subcaption{Ismenius Cavus, solar cell coverage area = \SI{2.4}{m^{2}}}
+    \label{fig:plot:sub:final-maximum-traverse-durations-ismenius-cavus}
+  \end{subfigure}\\[0.8ex]
+  \caption{Maximum traverse durations at mission sites. The same considerations were taken as in \refFig{fig:plot:ismenius-cavus-generated-energy-and-max-traverse-durations}.}
+  \label{fig:plot:final-maximum-traverse-durations-at-missions-sites}
+\end{figure}
+
+\ac{SA} sizing with the hibernation reference Sol power budget defined in \refTab{tab:hibernation-sol-power-budget} as the worst case power budget fails to meet the target \ac{SA} areas.
+However, the required power draws only differ by a few Watts.
+At Iani Chaos, this is achieved by reducing the hibernation mode power draws from \SI{18}{\watt} to \SI{17}{\watt}.
+At Ismenius Cavus, hibernation power draws need to be reduced from \SI{18}{\watt} to \SI{15}{\watt}.
+Taking into account a \SI{20}{\percent} system margin, the energy requirement for hibernation Sols become \SI{490}{\watt\hour} at Iani Chaos for a \SI{1.7}{m^{2}} \ac{SA} area and \SI{432}{\watt\hour} at Ismenius Cavus for a \SI{2.8}{m^{2}} \ac{SA} area.
+A first iteration of the rover with a \ac{SA} for an Ismenius Cavus deployment is showing in \refFig{fig:solar-array-on-ismenius-cavus-chaos}.
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=3.25in]{figures/images/ismenius-cavus-10deg-pitch.png}\\
+ \caption{Rover with \ac{SA} for Ismenius Cavus deployment.}
+ \label{fig:solar-array-on-ismenius-cavus-chaos}
+\end{figure}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Lorem ipsum dolor}
+\section{Simulation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The proposed rover and \ac{SA} configurations are modeled with Blender/Phobos and loaded into MARS for mission scenario simulation.
+Phobos is ``an add-on for the open-source 3D modeling software Blender that enables the creation of robot models for use in robot frameworks like ROS and ROCK or in real-time simulations such as MARS'' \cite{Phobos}.
+MARS is ``a cross-platform simulation and visualization tool created for robotics research.
+It consists of a core framework containing all main simulation components, a GUI (based on Qt), 3D visualization (using OSG) and a physics engine (based on ODE)'' \cite{MARSSim}.
 
-\subsection{Lorem}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\subsection{Z-Axis Revolutions}
 
-\subsection{Ipsum}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\refFig{fig:sub:simulation-data-rover-revolution-generated-power-line-chart} and \refFig{fig:sub:simulation-data-rover-revolution-generated-power-polar-chart} are two different representations of the same solar power output obtained from commanding the rover to execute a \SI{10}{\degree} forward body-pitch followed by several revolutions around its z-axis.
+These revolutions result in a sinusoidal power output variation.
+Local spikes and dips are noted around \SI{100}{\second} and \SI{160}{\second} due to small changes in the \ac{SA} inclination and orientation angles caused by the rover driving over uneven terrain.
+In \refFig{fig:sub:simulation-data-rover-revolution-generated-power-polar-chart}, the angle values represent the direction faced by the inclined \ac{SA}.
+Maximum power is generated when the \ac{SA} is oriented southwards, towards the equator, in the general direction of the sun.
+Inversely, facing northwards, away from the sun, generates the least amount of power.
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-\begin{figure}[H]
+\begin{figure}[h]
+  \captionsetup[subfigure]{justification=centering}
   \centering
-\includegraphics[width=3.25in]{Figures/Placeholder.png}\\
-\caption{\textbf{Lorem ipsum dolor sit amet}}
-\label{Fig1}
+  \setlength{\subfigureWidth}{0.24\textwidth}
+  \setlength{\graphicsHeight}{40mm}
+  \begin{subfigure}[t]{\subfigureWidth}
+    \centering
+    \includegraphics[height=\graphicsHeight]{figures/plots/zaxis-revolutions.png}
+    \subcaption{Line chart}
+    \label{fig:sub:simulation-data-rover-revolution-generated-power-line-chart}
+  \end{subfigure}\hfill
+  \begin{subfigure}[t]{\subfigureWidth}
+    \centering
+    \includegraphics[height=\graphicsHeight]{figures/plots/zaxis-revolutions-polar.png}
+    \subcaption{Polar chart}
+    \label{fig:sub:simulation-data-rover-revolution-generated-power-polar-chart}
+  \end{subfigure}\\[0.6ex]
+  \caption{Power generated by the rover's \ac{SA} for multiple revolutions along its z-axis.
+Simulation condition is solar noon at Ismenius Cavus with $\beta \approx \SI{10}{\degree}$.
+In the polar chart, angle values represent the direction faced by the inclined \ac{SA} where \SI{0}{\degree} is South (towards the equator), \SI{-90}{\degree} is East, \SI{180}{\degree} is North, and \SI{90}{\degree} is West.}
+  \label{fig:simulation-data-rover-revolution-generated-power}
 \end{figure}
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\subsection{Slope Compensation}
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+The worst case slope traverse is an on inclined surface facing away from the sun.
+The rover's active suspension system can be used to reduce the \ac{SA} inclination angle by commanding a rover body pitch in the opposite direction.
+This slope compensation scenario is illustrated in \refFig{fig:sub:rover-on-slope-beta} where $B$ denotes the slope surface inclination angle and $\beta$ the \ac{SA} surface inclination angle.
 
-\subsection{Dolor}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\begin{figure}[h]
+\captionsetup[subfigure]{justification=centering}
+  \centering
+  \begin{subfigure}[t]{\subfigureWidth}
+    \centering
+    \includegraphics[height=\graphicsHeight]{figures/images/stick-rover-beta-large.png}
+    \subcaption{$\beta = B$}
+    \label{fig:sub:rover-on-slope-beta-large}
+  \end{subfigure}\hfill
+  \begin{subfigure}[t]{\subfigureWidth}
+    \centering
+    \includegraphics[height=\graphicsHeight]{figures/images/stick-rover-beta-small.png}
+    \subcaption{$\beta < B$}
+    \label{fig:sub:rover-on-slope-beta-small}
+  \end{subfigure}\\[0.8ex]
+  \caption{Slope compensation with active suspension system to reduce the \ac{SA} surface inclination angle.
+Slope inclination angle $B = \SI{30}{\degree}$.
+In (a), $\beta = B = \SI{30}{\degree}$.
+In (b), the rover is tilted \SI{10}{\degree} in the opposite direction of the slope so that $\beta = \SI{20}{\degree}$.}
+  \label{fig:sub:rover-on-slope-beta}
+\end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Lorem ipsum dolor}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+By way of example, at Ismenius Cavus for a $\tau$ factor of 0.4 and an areocentric longitude $L_{s}$ of \SI{270}{\degree}, descending a \SI{30}{\degree} slope bearing North results in a daily insolation of \SI{319}{Whm^{-2}}.
+This is increased to \SI{767}{Whm^{-2}} by decreasing $\beta$ from \SI{30}{\degree} to \SI{25}{\degree} after tilting the rover southwards by \SI{5}{\degree} so that $\beta < B$.
+A \SI{10}{\degree} tilt would increase the daily insolation to \SI{1046}{Whm^{-2}} with $\beta = \SI{20}{\degree}$.
+The solar power generated from this scenario is simulated.
+\refFig{fig:sub:rover-on-slope-beta} shows solar power outputs for different body-pitch configuration while the rover is on a \SI{30}{\degree} slope.
+The initial state of the \ac{SA} $\beta$ inclination angle is equal to that of the slope angle.
+Two separate \SI{5}{\degree} forward pitch increments are executed at \SI{25}{\second} and \SI{35}{\second} which worsen solar power output by changing \ac{SA} $\beta$ inclination angle from ~\SI{30}{\degree} to ~\SI{40}{\degree}.
+Following that, four separate \SI{5}{\degree} backward pitch decrements are executed from \SI{45}{\second} to \SI{65}{\second}, progressively improving power generation as $\beta$ is changed from ~\SI{40}{\degree} to ~\SI{20}{\degree}.
+As a final task, the rover is commanded to drive forward at \SI{80}{\second} and it encounters uneven terrain which introduces minor fluctuations to the solar power output.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=3.25in]{figures/plots/slope-compensation.png}
+  \caption{Slope compensation with active suspension system to reduce the \ac{SA} surface inclination angle.
+Slope inclination angle $B = \SI{30}{\degree}$.
+In (a), $\beta = B = \SI{30}{\degree}$.
+In (b), the rover is tilted \SI{10}{\degree} in the opposite direction of the slope so that $\beta = \SI{20}{\degree}$.}
+  \label{fig:sub:rover-on-slope-beta}
+\end{figure}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+The findings of this thesis support using the SherpaTT rover active suspension system as a mechanism for solar panel inclination and orientation under certain \ac{SA} sizing conditions.
+Combining a maximum attainable \ac{SA} surface inclination angle of \SI{10}{\degree} with optimal daily orientation angles results in appreciable traverse gains when compared to what is obtained from a horizontal surface.
+However, this is not true for large \ac{SA} areas.
+Furthermore, the smaller the required solar cell coverage area the greater the gains.
+In light of this, \ac{SA} sizing for the the worst case daily insolations introduce a hibernation mode solar power draw constraint of \SI{17}{\watt} near the equator at \SI{2}{\degree}S and \SI{15}{\watt} in the northern hemisphere at \SI{34}{\degree}N.
+With these power budgets, an average traverse gain of \SI{34}{\percent} is achieved at \SI{2}{\degree}S for a clear day with a $\tau$ factor of 0.4.
+At \SI{34}{\degree}N, the average gain is \SI{25}{\percent} under the same atmospheric opacity.
+These gains remain significant on dusty days at \SI{23}{\percent} and \SI{10}{\percent} at respective latitudes with a $\tau$ factor of 1.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendices{}              % note there is no {} to put a title. Each appendix has its own title
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% For a single appendix, use the \appendix{} keyword and do not use the \section command.
+This paper presents an active suspension system use case that goes beyond negotiating complex terrains such as steep slopes or exploring crater environments.
+The following are a few suggested research topics that expands this idea:
 
-\section{Lorem ipsum dolor}        % first appendix
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\begin{itemize}
+  \item [(1)] Conducting a power budget cost-benefit analysis with respect to the power draws from the suspensions systems motors that are required to obtain the sun-facing inclined \ac{SA} surfaces power gains.
+  \item [(2)] Achieving higher pitch and rolls angles so that higher \ac{SA} surface inclination angles may be attained.
+  \item [(3)] Simulating ground adaption scenarios that preserve a desired \ac{SA} surface position into a fixed plane.
+  \item [(4)] Simulating shadowing events on the \ac{SA} and analyzing their affect on power outputs, in particular for shadows caused by the \ac{RA}.
+  \item [(5)] Implementing a battery model to simulate battery charge and discharge for a more complete power subsystem simulation.
+  \item [(6)] Developing power budgets for onboard instruments to simulate scenarios such as drilling for sample return missions.
+  \item [(7)] Proposing SherpaTT \ac{SA} designs for terrestrial and lunar mission scenarios.
+  \item [(8)] Exploring other alternative use cases for the rover's active suspension system such as nighttime star tracking for astronomical observations with a mounted telescope.
+\end{itemize}
 
@@
 
-\bibitem{BIB_01}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+\bibitem{Cordes2018a}
+Cordes, F.
+Design and Experimental Evaluation of a Hybrid Wheeled-Leg Exploration Rover in the Context of Multi-Robot Systems.
+PhD thesis, University of Bremen.
+2018, https://doi.org/10.13140/RG.2.2.24973.79843
 
-\bibitem{BIB_02}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+\bibitem{Cordes2018b}
+Cordes, F, Kirchner, F, Babu, A.
+Design and field testing of a rover with an actively articulated suspension system in a Mars analog terrain.
+J Field Robotics.
+2018; 35: 1149– 1181.
+https://doi.org/10.1002/rob.21808
 
-\bibitem{BIB_03}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+\bibitem{Labreche2020}
+Labrèche, G.
+Exploiting the SherpaTT Rover Active Suspension System to Enable Optimal Solar Array Inclination and Orientation for Long Traverses in a Martian Environment.
+2020, http://urn.kb.se/resolve?urn=urn:nbn:se:ltu:diva-78016
+
+\bibitem{Phobos}
+DFKI/RIC, Phobos. https://github.com/dfki-ric/phobos. Accessed on: Jun. 12, 2020.
+
+\bibitem{MARSSim}
+DFKI/RIC, MARS - Machina Arte Robotum Simulans. https://robotik.dfki-bremen.de/en/research/softwaretools/mars.html. Accessed on: Jun. 12, 2020.
 

### 2020-06-12 tables/worst-case-power-budget-flat-traverse-sol-tau-1.tex
First draft of the paper.

\begin{table}[h]
  \footnotesize
  \centering
  \caption{Worst case flat traverse Sol power budget, $\tau$\,=\,1 and $\beta$\,=\,\SI{10}{\degree}.}
  \label{tab:worst-case-traverse-sol-power-budget}
  \begin{tabular}{lc|c|c|c|c|}
    \cline{3-6}
     & & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}Iani Chaos\\ $Ls=\SI{81}{\degree}$\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}Ismenius Cavus\\ $Ls=\SI{273}{\degree}$\end{tabular}} \\ \hline
    \multicolumn{1}{|l|}{Mode} & P {[}W{]} & t {[}min{]} & E {[}Wh{]} & t {[}min{]} & E {[}Wh{]} \\ \hline
    \multicolumn{1}{|l|}{Idle - Day} & 29 & 603 & 291 & 464 & 224 \\ \hline
    \multicolumn{1}{|l|}{Communication} & 52 & 35 & 30 & 35 & 30 \\ \hline
    \multicolumn{1}{|l|}{Traverse} & 113 & 4.8 & 9 & 4.8 & 9 \\ \hline
    \multicolumn{1}{|l|}{Science Stop} & 60 & 60 & 60 & 60 & 60 \\ \hline
    \multicolumn{1}{|l|}{Optimal Pose} & 75 & 12 & 13 & 10 & 13 \\ \hline
    \multicolumn{1}{|l|}{Idle - Night} & 20 & 242 & 242 & 866 & 289 \\ \hline
    \multicolumn{1}{|r|}{Total} & 349 & 1440 & 646 & 1440 & 625 \\ \hline
    \multicolumn{1}{|r|}{+20\% Margin} & 419 & - & 775 & - & 750 \\ \hline
  \end{tabular}
\end{table}

### 2020-06-12 make.sh

@@ -1,2 +1,0 @@
-#!/bin/bash
-pdflatex Article.tex

### 2020-06-12 article.tex
Minor text corrections.

--- 2020-06-12 Article.tex
@@
 Taking into account a \SI{20}{\percent} system margin, the energy requirement for hibernation Sols become \SI{490}{\watt\hour} at Iani Chaos for a \SI{1.7}{m^{2}} \ac{SA} area and \SI{432}{\watt\hour} at Ismenius Cavus for a \SI{2.8}{m^{2}} \ac{SA} area.
-A first iteration of the rover with a \ac{SA} for an Ismenius Cavus deployment is showing in \refFig{fig:solar-array-on-ismenius-cavus-chaos}.
+A first iteration of the rover with a \ac{SA} for an Ismenius Cavus deployment is shown in \refFig{fig:solar-array-on-ismenius-cavus-chaos}.
 
@@
 \refFig{fig:sub:rover-on-slope-beta} shows solar power outputs for different body-pitch configuration while the rover is on a \SI{30}{\degree} slope.
-The initial state of the \ac{SA} $\beta$ inclination angle is equal to that of the slope angle.
-Two separate \SI{5}{\degree} forward pitch increments are executed at \SI{25}{\second} and \SI{35}{\second} which worsen solar power output by changing \ac{SA} $\beta$ inclination angle from ~\SI{30}{\degree} to ~\SI{40}{\degree}.
-Following that, four separate \SI{5}{\degree} backward pitch decrements are executed from \SI{45}{\second} to \SI{65}{\second}, progressively improving power generation as $\beta$ is changed from ~\SI{40}{\degree} to ~\SI{20}{\degree}.
+The initial state of the \ac{SA} surface inclination angle is equal to that of the slope angle.
+Two separate \SI{5}{\degree} forward pitch increments are executed at \SI{25}{\second} and \SI{35}{\second} which worsen solar power output by changing the \ac{SA} surface inclination angle from $\sim$\SI{30}{\degree} to $\sim$\SI{40}{\degree}.
+Four separate \SI{5}{\degree} backward pitch decrements are executed from \SI{45}{\second} to \SI{65}{\second}, progressively improving power generation as $\beta$ is decreased from $\sim$\SI{40}{\degree} to $\sim$\SI{20}{\degree}.
 As a final task, the rover is commanded to drive forward at \SI{80}{\second} and it encounters uneven terrain which introduces minor fluctuations to the solar power output.

### 2020-06-12 article.tex
replaced 'thesis' to 'paper'.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The findings of this thesis support using the SherpaTT rover active suspension system as a mechanism for solar panel inclination and orientation under certain \ac{SA} sizing conditions.
+The findings of this paper support using the SherpaTT rover active suspension system as a mechanism for solar panel inclination and orientation under certain \ac{SA} sizing conditions.
 Combining a maximum attainable \ac{SA} surface inclination angle of \SI{10}{\degree} with optimal daily orientation angles results in appreciable traverse gains when compared to what is obtained from a horizontal surface.

### 2020-06-22 article.tex
minor text fixes

@@
 Georges L. J. Labrèche\\
-Lorem ipsum dolor sit amet\\
-Consectetur adipiscing\\
-12345 Eiusmod, Tempor\\
 Georges.Labreche@gmail.com
 \and
-Dr. Florian Cordes\\
+Florian Cordes\\
 DFKI Robotics Innovation Center\\
@@
 
-\tableofcontents
+% Table of content is not needed.
+% \tableofcontents
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The exploration rover SherpaTT has a total mass of approximately \SI{160}{\kilo\gram} and the legs as well as the \ac{RA} weigh about \SI{25}{\kilo\gram} each.
+The exploration rover SherpaTT has a total mass of approximately \SI{206}{\kilo\gram} and the legs as well as the \ac{RA} weigh about \SI{25}{\kilo\gram} each.
 The wheeled-leg active suspension system allows the rover to assume different poses with varying inertial moments.
@@
 Large inclination angles are typically preferred with respect to increased insolation for a sun-facing surface.
-However, constraints on the rover's active suspension system imposes a limit on the achievable body pitch angle.
+However, constraints on the rover's active suspension system impose a limit on the achievable body pitch angle.
 Body pitch commands of up to \SI{10}{\degree} are experimentally evaluated during steep slope climbing in \cite{Cordes2018a}.
@@
 
-\refTab{tab:insolation-iani-chaos-clear-and-dusty-days} and \refTab{tab:insolation-ismenius-cavus-clear-and-dusty-days} presents the best and worst case daily insolations $H_{h}$, on horizontal \ac{SA} surface, compared to those obtained with $H_{\beta}$, on an inclined sun-facing \ac{SA} surface.
+\refTab{tab:insolation-iani-chaos-clear-and-dusty-days} and \refTab{tab:insolation-ismenius-cavus-clear-and-dusty-days} present the best and worst case daily insolations $H_{h}$, on horizontal \ac{SA} surface, compared to those obtained with $H_{\beta}$, on an inclined sun-facing \ac{SA} surface.
 Optical depths $\tau$ for clear to dusty days are evaluated with the daily insolations expressed in \si{Wh.m^{-2}} and the gains in percentage.
@@
 Durations of daylight dependent modes in the traverse reference Sol are based on the total length of daylight time for worst case daily insolations Sols presented in \refTab{tab:insolation-iani-chaos-clear-and-dusty-days} and \refTab{tab:insolation-ismenius-cavus-clear-and-dusty-days} with $\tau$ factor 1 and $\beta=\SI{10}{\degree}$ for the \ac{SA} surface inclination angle.
-Propulsion power draws for the rover's flat terrain traverse mode is determined from data collected during the SherpaTT Utah field trial.
+Propulsion power draws for the rover's flat terrain traverse mode is determined from data collected during the SherpaTT Utah field trial \cite{Cordes2018b}.
 
@@
 
-To explain the lack of significant gains, the generated \ac{SA} energy and maximum traverse durations is plotted in \refFig{fig:plot:ismenius-cavus-generated-energy-and-max-traverse-durations} for Ismenius Cavus.
+To explain the lack of significant gains, the generated \ac{SA} energy and maximum traverse durations are plotted in \refFig{fig:plot:ismenius-cavus-generated-energy-and-max-traverse-durations} for Ismenius Cavus.
 During clear days at $\tau$ factor 0.4, a ceiling is imposed on the daily maximum traverse durations due to the available daylight time for traversing.
@@
 
-To resolve this, the worst case power budget in \refTab{tab:worst-case-traverse-sol-power-budget} is set aside and the \ac{SA} sizing process is approached inversely by identifying solar cell coverage area targets based on the traverse distance gains brought about by an inclined surface.
+The worst case power budget in \refTab{tab:worst-case-traverse-sol-power-budget} is set aside and the \ac{SA} sizing process is approached inversely by identifying solar cell coverage area targets based on the traverse distance gains brought about by an inclined surface.
 \refFig{fig:plot:flat-traverse-gains-for-different-sa-area} compares the traverse distance gains obtained with an inclined \ac{SA} surface for different solar cell coverage areas and optical depths.
@@
 
-The worst case slope traverse is an on inclined surface facing away from the sun.
+The worst case slope traverse is on an inclined surface facing away from the sun.
 The rover's active suspension system can be used to reduce the \ac{SA} inclination angle by commanding a rover body pitch in the opposite direction.

### 2020-06-22 article.tex
text fix

@@
 \begin{itemize}
-  \item [(1)] Conducting a power budget cost-benefit analysis with respect to the power draws from the suspensions systems motors that are required to obtain the sun-facing inclined \ac{SA} surfaces power gains.
+  \item [(1)] Conducting a power budget cost-benefit analysis with respect to the power draws from the suspension systems motors that are required to obtain the sun-facing inclined \ac{SA} surfaces power gains.
   \item [(2)] Achieving higher pitch and rolls angles so that higher \ac{SA} surface inclination angles may be attained.

### 2020-06-24 article.tex
sync with overleaf

@@
 
+% URL hyperlinks in References section.
+\usepackage{hyperref}
+
+%\hypersetup{
+%  colorlinks=true,
+%  linkcolor=blue,
+%  filecolor=magenta,
+%  urlcolor=cyan,
+%}
+
+%\urlstyle{same}
+
 % New commands.
@@
 % Renew commands.
+
+% Use alpha for footnotes.
 \renewcommand\thefootnote{{(\alph{footnote})}} % footnote formatting and colors
@@
 \and
-Florian Cordes\\
-DFKI Robotics Innovation Center\\
-Robert-Hooke-Straße 1\\
-28359 Bremen, Germany\\
+Florian Cordes\footnote{DFKI Robotics Innovation Center, Robert-Hooke-Straße 1, 28359 Bremen, Germany.}\\
 Florian.Cordes@dfki.de
 }
+
+% Extra vertical spacing in table cells.
+%{\renewcommand{\arraystretch}{1.5}% for the vertical padding
 
@@
   \centering
-  \includegraphics[width=2.9in]{figures/images/sherpatt-actively-articulated-suspension-sytem.png}\\
+  \includegraphics[width=3.2in]{figures/images/sherpatt-actively-articulated-suspension-sytem.png}\\
   \caption{Description of DoF present in SherpaTT’s
@@
 The actively articulated suspension system consists of four wheeled-legs with a total of 20 motors.
-The distribution of motors across a single leg is shown in \refFig{fig:sherpatt-actively-articulated-suspension-system}.
+Motor distribution across a single leg is shown in \refFig{fig:sherpatt-actively-articulated-suspension-system}.
 Each leg is equipped with three suspension motors and two drive motors.
 The suspension motors are responsible for Pan, \ac{IL}, and \ac{OL} revolute joint rotations whereas the drive motors are responsible for \ac{WS} and \ac{WD}.
+A first design iteration of the rover with \ac{SA} for an Ismenius Cavus deployment is shown in \refFig{fig:solar-array-on-ismenius-cavus-chaos}.
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=2.8in]{figures/images/ismenius-cavus-10deg-pitch.png}\\
+ \caption{Rover with \ac{SA} for Ismenius Cavus deployment.}
+ \label{fig:solar-array-on-ismenius-cavus-chaos}
+\end{figure}
 
@@
 Optical depths $\tau$ for clear to dusty days are evaluated with the daily insolations expressed in \si{Wh.m^{-2}} and the gains in percentage.
-The solar insolation values are taken from \cite{Labreche2020}.
+The solar insolation values are taken from \cite{Labreche2020} and obtained with Mars solar radiation formulas in \cite{Appelbaum1989}, \cite{Appelbaum1990}, \cite{Appelbaum1991}, \cite{Appelbaum1993}, and \cite{Appelbaum1994}.
 
@@
 
-Gains obtained in daily insolation with an inclined surface are more pronounced for sites further away from the equator.
-For a typical optical depth of $\tau = 0.4$, the average daily insolation gain on the inclined surface is approximately \SI{7}{\percent} at Iani Chaos and \SI{9}{\percent} at Ismenius Cavus.
-Due to the mostly diffuse composition of solar irradiance at higher optical depths, inclined surfaces become irrelevant during global dust storms.
+Daily insolation gains obtained with an inclined surface are more pronounced for sites further away from the equator.
+For a typical optical depth of $\tau$ factor 0.4, the average daily insolation gain on the inclined surface is approximately \SI{7}{\percent} at Iani Chaos and \SI{9}{\percent} at Ismenius Cavus.
+The mostly diffuse composition of solar irradiance at higher optical depths make inclined surfaces irrelevant in global dust storms.
 For $\tau \geq 2$, gains in daily insolation become negligible at both sites.
+
+\input{tables/power-budget-hibernation-sol.tex}
 
@@
 Hibernation power draws are identical during day and nighttime so the hibernation reference Sol does not have a best or worse case Sol with respect to available sunlight.
-
-\input{tables/power-budget-hibernation-sol.tex}
 
@@
     \label{fig:plot:sub:ismenius-cavus-max-traverse-durations}
-  \end{subfigure}\\[0.8ex]
+  \end{subfigure}
   \caption{Generated energy and maximum flat terrain traverse duration at Ismenius Cavus with solar cell coverage area of \SI{4.1}{m^{2}}.
@@
     \label{fig:plot:sub:iani-chaos-max-traverse-durations}
-  \end{subfigure}\\[0.8ex]
+  \end{subfigure}
   \caption{Generated energy and maximum flat terrain traverse duration at Iani Chaos with solar cell coverage area of \SI{2.3}{m^{2}}.
@@
     \label{fig:plot:sub:iani-chaos-flat-traverse-gains-for-different-sa-area}
-    \end{subfigure}\\[0.8ex]
+    \end{subfigure}
     \caption{Average flat terrain traverse distance gains at mission sites for different solar cell coverage areas.
@@
     \label{fig:plot:sub:final-maximum-traverse-durations-ismenius-cavus}
-  \end{subfigure}\\[0.8ex]
+  \end{subfigure}
   \caption{Maximum traverse durations at mission sites. The same considerations were taken as in \refFig{fig:plot:ismenius-cavus-generated-energy-and-max-traverse-durations}.}
@@
 Taking into account a \SI{20}{\percent} system margin, the energy requirement for hibernation Sols become \SI{490}{\watt\hour} at Iani Chaos for a \SI{1.7}{m^{2}} \ac{SA} area and \SI{432}{\watt\hour} at Ismenius Cavus for a \SI{2.8}{m^{2}} \ac{SA} area.
-A first iteration of the rover with a \ac{SA} for an Ismenius Cavus deployment is shown in \refFig{fig:solar-array-on-ismenius-cavus-chaos}.
+\refFig{fig:rover-body-redesign} shows the rover's body redesign from a pyramid to a cubic shape in order to better accommodate the \ac{SA} surface and avoid shadowing.
 
 \begin{figure}[h]
+\captionsetup[subfigure]{justification=centering}
   \centering
- \includegraphics[width=3.25in]{figures/images/ismenius-cavus-10deg-pitch.png}\\
- \caption{Rover with \ac{SA} for Ismenius Cavus deployment.}
- \label{fig:solar-array-on-ismenius-cavus-chaos}
+  \setlength{\subfigureWidth}{0.24\textwidth}
+  \setlength{\graphicsHeight}{29mm}
+  \begin{subfigure}[t]{\subfigureWidth}
+    \centering
+    \includegraphics[height=\graphicsHeight]{figures/images/body-before.png}
+    \subcaption{Before}
+    \label{fig:sub:rover-body-redesign-before}
+    \end{subfigure}\hfill
+  \begin{subfigure}[t]{\subfigureWidth}
+    \centering
+    \includegraphics[height=\graphicsHeight]{figures/images/body-after.png}
+    \subcaption{After}
+    \label{fig:sub:rover-body-redesign-after}
+  \end{subfigure}
+  \caption{Rover body redesign.}
+  \label{fig:rover-body-redesign}
 \end{figure}
@@
 Inversely, facing northwards, away from the sun, generates the least amount of power.
+These are the expected results thus validating the simulation environment for further development and mission scenario analysis.
 
@@
     \label{fig:sub:rover-on-slope-beta-small}
-  \end{subfigure}\\[0.8ex]
+  \end{subfigure}
   \caption{Slope compensation with active suspension system to reduce the \ac{SA} surface inclination angle.
@@
 
+At the time of writing this paper, work is already being done in (5) as part of the ADE (OG10) project for autonomous decision making in very long traverses 
+\cite{ADEOG10}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 PhD thesis, University of Bremen.
-2018, https://doi.org/10.13140/RG.2.2.24973.79843
+2018, \url{https://doi.org/10.13140/RG.2.2.24973.79843}
 
@@
 Design and field testing of a rover with an actively articulated suspension system in a Mars analog terrain.
-J Field Robotics.
+Journal of Field Robotics.
 2018; 35: 1149– 1181.
-https://doi.org/10.1002/rob.21808
+\url{https://doi.org/10.1002/rob.21808}
 
@@
 Exploiting the SherpaTT Rover Active Suspension System to Enable Optimal Solar Array Inclination and Orientation for Long Traverses in a Martian Environment.
-2020, http://urn.kb.se/resolve?urn=urn:nbn:se:ltu:diva-78016
+2020, \url{http://urn.kb.se/resolve?urn=urn:nbn:se:ltu:diva-78016}
+
+\bibitem{Appelbaum1989}
+Appelbaum, J, Flood, D. Solar Radiation on Mars. NASA-TM-102299. 1989, \url{https://ntrs.nasa.gov/?R=19890018252}
+
+\bibitem{Appelbaum1990}
+Appelbaum, J, Flood, D. Solar radiation on Mars: Update 1990. NASA-TM-103623. 1990, \url{https://ntrs.nasa.gov/?R=19910005804}
+
+\bibitem{Appelbaum1991}
+Appelbaum, J, Flood, D. Solar radiation on Mars: Update 1991. NASA-TM-105216. 1991, \url{https://ntrs.nasa.gov/?R=19910023732}
+
+\bibitem{Appelbaum1993}
+Appelbaum, J, Sherman, I, Landis, G. A. Solar radiation on Mars: Stationary photovoltaic array. NASA-TM-106321. 1993, \url{https://ntrs.nasa.gov/?R=19940010257}
+
+\bibitem{Appelbaum1994}
+Appelbaum, J, Flood, D, Norambuena, M. Solar radiation on Mars: Tracking photovoltaic array. NASA-TM-106700. 1994, \url{https://ntrs.nasa.gov/?R=19950004977}
 
 \bibitem{Phobos}
-DFKI/RIC, Phobos. https://github.com/dfki-ric/phobos. Accessed on: Jun. 12, 2020.
+DFKI/RIC, Phobos. \url{https://github.com/dfki-ric/phobos}. Accessed on: Jun. 12, 2020.
 
 \bibitem{MARSSim}
-DFKI/RIC, MARS - Machina Arte Robotum Simulans. https://robotik.dfki-bremen.de/en/research/softwaretools/mars.html. Accessed on: Jun. 12, 2020.
+DFKI/RIC, MARS - Machina Arte Robotum Simulans. \url{https://robotik.dfki-bremen.de/en/research/softwaretools/mars.html}. Accessed on: Jun. 12, 2020.
+
+\bibitem{ADEOG10}
+DFKI/RIC, ADE (OG10) - Autonomous Decision Making in Very Long Traverses. \url{https://robotik.dfki-bremen.de/en/research/projects/ade-og10.html}. Accessed on: Jun. 23, 2020.
 

### 2020-06-24 extended_abstract.tex
sync with overleaf

--- 2020-06-24 article.tex
@@
 \newcommand{\refTab}[1]{{Table}~\ref{#1}}  % Command for table reference.
+
+% For block commenting
+\newcommand{\comment}[1]{}
 
@@
 
-\begin{abstract}
 The SherpaTT rover is prepared for further autonomous long distance traverses in terrain akin to the Martian environment.
@@
 This results in traverse gains of up to \SI{34}{\percent} and \SI{25}{\percent} for clear days at Iani Chaos and Ismenius Cavus, respectively.
-\end{abstract}
 
-% Table of content is not needed.
-% \tableofcontents
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The exploration rover SherpaTT has a total mass of approximately \SI{206}{\kilo\gram} and the legs as well as the \ac{RA} weigh about \SI{25}{\kilo\gram} each.
@@
 
+\comment{
 \begin{figure}[h]
@@
 \end{figure}
+}
 
-The actively articulated suspension system consists of four wheeled-legs with a total of 20 motors.
-Motor distribution across a single leg is shown in \refFig{fig:sherpatt-actively-articulated-suspension-system}.
-Each leg is equipped with three suspension motors and two drive motors.
+The active suspension system consists of four wheeled-legs with a total of 20 motors.\comment{Motor distribution across a single leg is shown in \refFig{fig:sherpatt-actively-articulated-suspension-system}.} Each leg is equipped with three suspension motors and two drive motors.
 The suspension motors are responsible for Pan, \ac{IL}, and \ac{OL} revolute joint rotations whereas the drive motors are responsible for \ac{WS} and \ac{WD}.
-A first design iteration of the rover with \ac{SA} for an Ismenius Cavus deployment is shown in \refFig{fig:solar-array-on-ismenius-cavus-chaos}.
+\comment{A first design iteration of the rover with \ac{SA} for an Ismenius Cavus deployment is shown in \refFig{fig:solar-array-on-ismenius-cavus-chaos}.}
 
+\comment{
 \begin{figure}[h]
@@
 \end{figure}
+}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Power Budget}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Large inclination angles are typically preferred with respect to increased insolation for a sun-facing surface.
-However, constraints on the rover's active suspension system impose a limit on the achievable body pitch angle.
-Body pitch commands of up to \SI{10}{\degree} are experimentally evaluated during steep slope climbing in \cite{Cordes2018a}.
-Modeling higher pitch angles resulted in poor wheel-ground contact angle due to the \ac{WS} axis having the same tilt as the rover's body.
-The attainable tilt is thus restricted resulting in a maximum \ac{SA} surface inclination angle of $\beta = \SI{10}{\degree}$.
-
-\input{tables/insolation-iani-chaos-clear-and-dusty-days.tex}
-
-\refTab{tab:insolation-iani-chaos-clear-and-dusty-days} and \refTab{tab:insolation-ismenius-cavus-clear-and-dusty-days} present the best and worst case daily insolations $H_{h}$, on horizontal \ac{SA} surface, compared to those obtained with $H_{\beta}$, on an inclined sun-facing \ac{SA} surface.
-Optical depths $\tau$ for clear to dusty days are evaluated with the daily insolations expressed in \si{Wh.m^{-2}} and the gains in percentage.
-The solar insolation values are taken from \cite{Labreche2020} and obtained with Mars solar radiation formulas in \cite{Appelbaum1989}, \cite{Appelbaum1990}, \cite{Appelbaum1991}, \cite{Appelbaum1993}, and \cite{Appelbaum1994}.
-
-\input{tables/insolation-ismenius-cavus-clear-and-dusty-days.tex}
-
-Daily insolation gains obtained with an inclined surface are more pronounced for sites further away from the equator.
-For a typical optical depth of $\tau$ factor 0.4, the average daily insolation gain on the inclined surface is approximately \SI{7}{\percent} at Iani Chaos and \SI{9}{\percent} at Ismenius Cavus.
-The mostly diffuse composition of solar irradiance at higher optical depths make inclined surfaces irrelevant in global dust storms.
-For $\tau \geq 2$, gains in daily insolation become negligible at both sites.
-
-\input{tables/power-budget-hibernation-sol.tex}
-
-As a prerequisite to \ac{SA} sizing, power budgets are defined for hibernation and flat terrain traverse reference Sols.
-These are presented in \refTab{tab:hibernation-sol-power-budget} and \refTab{tab:worst-case-traverse-sol-power-budget}.
-Hibernation power draws are identical during day and nighttime so the hibernation reference Sol does not have a best or worse case Sol with respect to available sunlight.
-
-Durations of daylight dependent modes in the traverse reference Sol are based on the total length of daylight time for worst case daily insolations Sols presented in \refTab{tab:insolation-iani-chaos-clear-and-dusty-days} and \refTab{tab:insolation-ismenius-cavus-clear-and-dusty-days} with $\tau$ factor 1 and $\beta=\SI{10}{\degree}$ for the \ac{SA} surface inclination angle.
-Propulsion power draws for the rover's flat terrain traverse mode is determined from data collected during the SherpaTT Utah field trial \cite{Cordes2018b}.
-
-\input{tables/worst-case-power-budget-flat-traverse-sol-tau-1.tex}
-
-The \textit{Optimal Pose} mode in \refTab{tab:worst-case-traverse-sol-power-budget} consists of using the rover's active suspension system to reconfigure the \ac{SA} surface orientation and inclination so that daily insolation is maximized on the following Sol.
-In this manner, the suspension system undertakes the role of a 2-axis solar tracking mechanism.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Solar Array Sizing}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The solar cell coverage area $A$ is expressed as:
-
-\begin{equation}
-  \label{eq:solar_cell_coverage_area}
-  A = \frac{E}{\eta \cdot H \cdot PR}
-\end{equation}
-
-where $E$ is the rover's energy requirement, $\eta$ is the solar cell efficiency, $H$ is the daily insolation, and $PR$ is the solar cell performance ratio.
-An initial \ac{SA} sizing is determined with $H_{\beta}$ from \refTab{tab:insolation-iani-chaos-clear-and-dusty-days} and \refTab{tab:insolation-ismenius-cavus-clear-and-dusty-days} as well as $E$ from \refTab{tab:worst-case-traverse-sol-power-budget} for the worst case daily insolation at $\tau$ factor 1.
-\ac{EOL} values for $PR$ and $\eta$ are determined in \cite{Labreche2020}:
-
-\begin{itemize}
-  \item [(1)] $H$\,$=$\,\SI{2479}{Wh.m^{-2}} and $E$\,$=$\,\SI{775}{\watt\hour} at Iani Chaos.
-  \item [(2)] $H$\,$=$\,\SI{1345}{Wh.m^{-2}} and $E$\,$=$\,\SI{750}{\watt\hour} at Ismenius Cavus.
-  \item [(3)] $PR_{EOL}$\,$=$\,0.62.
-  \item [(4)] $\eta_{EOL}$\,$=$\,0.22.
-\end{itemize}
-
-Furthermore, the solar cell packing efficiency is assumed at \SI{85}{\percent}, the \ac{SA} surface density at \SI{3.7}{kg.m^{-2}}, and the average slippage at \SI{15}{\percent} when traversing a flat terrains for any given distance.
-Traversing is constrained to daylight hours and it is assumed that on average traversing only occurs every third Sol.
-
-At Iani Chaos, the required \ac{SA} area is \SI{2.7}{m^{2}} and the mass 9.95 \si{\kilo\gram}.
-\ac{SA} surface inclination of \SI{10}{\degree} with a daily sun-facing reorientation results in a \ac{SA} size decrease of \SI{3.9}{\percent} when compared against a horizontal surface configuration.
-The maximum flat traverse distance achievable over the course of a Martian year is increased by \SI{13.22}{\percent} from \SI{42.43}{\kilo\meter} to \SI{48.04}{\kilo\meter} with $\tau$ factor 1 during global dust storm season and 0.4 otherwise.
-At Ismenius Cavus, the required \ac{SA} area is \SI{4.8}{m^{2}}, its mass 17.8 \si{\kilo\gram}, and a \SI{4.6}{\percent} \ac{SA} size decrease is achieved.
-The maximum flat traverse distance achievable over the course of a Martian year is increased by \SI{2.13}{\percent} from \SI{63.05}{\kilo\meter} to \SI{64.39}{\kilo\meter}.
-
-The traverse distance gains attributed to \ac{SA} inclination capabilities do not justify taking advantage of the rover's active suspension system for the purpose of increasing solar power generation.
-This is particularly true at Ismenius Cavus.
-The savings in \ac{SA} size and mass also leave much to be desired.
-Furthermore, the large \ac{SA} are problematic in terms of rover integration.
-This is illustrated in \refFig{fig:sa-area-initial-sizes}.
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=3.25in]{figures/images/sa-area-initial-sizes.png}\\
-  \caption{Initial \ac{SA} sizing. The outlined square areas are equivalent to \ac{SA} areas of \SI{2.7}{m^{2}} for Iani Chaos and \SI{4.8}{m^{2}} for Ismenius Cavus.}
-  \label{fig:sa-area-initial-sizes}
-\end{figure}
-
-To explain the lack of significant gains, the generated \ac{SA} energy and maximum traverse durations are plotted in \refFig{fig:plot:ismenius-cavus-generated-energy-and-max-traverse-durations} for Ismenius Cavus.
-During clear days at $\tau$ factor 0.4, a ceiling is imposed on the daily maximum traverse durations due to the available daylight time for traversing.
-The maximum traverse time is already attained with a horizontal \ac{SA}, making an inclined \ac{SA} irrelevant in terms traverse distance gains.
-As seen in \refFig{fig:plot:sub:ismenius-cavus-max-traverse-durations}, the inclined \ac{SA} is only slightly advantageous during the global dust storm season with a $\tau$ factor of 1.
-
-\begin{figure}[h]
-\captionsetup[subfigure]{justification=centering}
-  \centering
-  \setlength{\subfigureWidth}{0.24\textwidth}
-  \setlength{\graphicsHeight}{40mm}
-  \begin{subfigure}[t]{\subfigureWidth}
-    \centering
-    \includegraphics[height=\graphicsHeight]{figures/plots/ismeniuscavus-daily-generated-energy-for-solar-cell-coverage-area-41m2.png}
-    \subcaption{Generated Energy}
-    \label{fig:plot:sub:ismenius-cavus-generated-energy}
-  \end{subfigure}\hfill
-  \begin{subfigure}[t]{\subfigureWidth}
-    \centering
-    \includegraphics[height=\graphicsHeight]{figures/plots/ismeniuscavus-75w-max-traverse-durations-for-solar-cell-coverage-area-41m2.png}
-    \subcaption{Maximum Traverse Durations}
-    \label{fig:plot:sub:ismenius-cavus-max-traverse-durations}
-  \end{subfigure}
-  \caption{Generated energy and maximum flat terrain traverse duration at Ismenius Cavus with solar cell coverage area of \SI{4.1}{m^{2}}.
-Surface inclination angle $\beta$ is \SI{10}{\degree}.
-$\tau$ factor 1 is used for global dust storm season ($\SI{185}{\degree} \leq L_{s} \leq \SI{315}{\degree}$) and 0.4 otherwise.
-The \textit{available daylight traverse time} corresponds to the amount of daylight hours left in a \textit{Traverse Sol} after subtracting the time taken by rover modes unrelated to traversing.}
-  \label{fig:plot:ismenius-cavus-generated-energy-and-max-traverse-durations}
-\end{figure}
-
-However, no such ceiling can be observed for Iani Chaos in \refFig{fig:plot:iani-chaos-generated-energy-and-max-traverse-durations} which would explain the poor gains for that mission site scenario.
-In both cases, lack of traverse distance gains is more closely tied to the $\tau$ factor selected when defining the worst case reference Sol that drives \ac{SA} sizing.
-At high optical opacities, increased light scattering by airborne Martian dust results in $H_{\beta} \approx H_{h}$ due to diffuse insolation being the largest component in the global insolation.
-Thus, when \ac{SA} sizing for power generation during dusty Sols, the resulting inclined \ac{SA} surface yield little to no benefits over horizontal surfaces with respect to traverse distance gains as well as \ac{SA} mass and area.
-
-\begin{figure}[h]
-\captionsetup[subfigure]{justification=centering}
-  \centering
-  \setlength{\subfigureWidth}{0.24\textwidth}
-  \setlength{\graphicsHeight}{40mm}
-  \begin{subfigure}[t]{\subfigureWidth}
-    \centering
-    \includegraphics[height=\graphicsHeight]{figures/plots/ianichaos-daily-generated-energy-for-solar-cell-coverage-area-23m2.png}
-    \subcaption{Generated Energy}
-    \label{fig:plot:sub:iani-chaos-generated-energy}
-  \end{subfigure}\hfill
-  \begin{subfigure}[t]{\subfigureWidth}
-    \centering
-    \includegraphics[height=\graphicsHeight]{figures/plots/ianichaos-75w-max-traverse-durations-for-solar-cell-coverage-area-23m2.png}
-    \subcaption{Maximum Traverse Durations}
-    \label{fig:plot:sub:iani-chaos-max-traverse-durations}
-  \end{subfigure}
-  \caption{Generated energy and maximum flat terrain traverse duration at Iani Chaos with solar cell coverage area of \SI{2.3}{m^{2}}.
-The same considerations were taken as in \refFig{fig:plot:ismenius-cavus-generated-energy-and-max-traverse-durations}.}
-  \label{fig:plot:iani-chaos-generated-energy-and-max-traverse-durations}
-\end{figure}
-
-The worst case power budget in \refTab{tab:worst-case-traverse-sol-power-budget} is set aside and the \ac{SA} sizing process is approached inversely by identifying solar cell coverage area targets based on the traverse distance gains brought about by an inclined surface.
-\refFig{fig:plot:flat-traverse-gains-for-different-sa-area} compares the traverse distance gains obtained with an inclined \ac{SA} surface for different solar cell coverage areas and optical depths.
-
-\begin{figure}[h]
-\captionsetup[subfigure]{justification=centering}
-  \centering
-  \setlength{\subfigureWidth}{0.24\textwidth}
-  \setlength{\graphicsHeight}{40mm}
-    \begin{subfigure}[t]{\subfigureWidth}
-      \centering
-      \includegraphics[height=\graphicsHeight]{figures/plots/ianichaos-75w-traverse-gains-for-different-solar-cell-coverage-areas.png}
-    \subcaption{Iani Chaos}
-    \label{fig:plot:sub:ismenius-chaos-flat-traverse-gains-for-different-sa-area}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{\subfigureWidth}
-      \centering
-      \includegraphics[height=\graphicsHeight]{figures/plots/ismeniuscavus-75w-traverse-gains-for-different-solar-cell-coverage-areas.png}
-    \subcaption{Ismenius Cavus}
-    \label{fig:plot:sub:iani-chaos-flat-traverse-gains-for-different-sa-area}
-    \end{subfigure}
-    \caption{Average flat terrain traverse distance gains at mission sites for different solar cell coverage areas.
-\ac{SA} inclination angle $\beta_{max} = \SI{10}{\degree}$ with orientation angles $\gamma_{c}$ set to their optimal values for the considered traverse Sols.}
-    \label{fig:plot:flat-traverse-gains-for-different-sa-area}
-\end{figure}
-
-Targeting a solar cell coverage area of \SI{1.5}{m^{2}} at Iani Chaos results in an average \SI{34}{\percent} gain in traverse for a clear day at $\tau$ factor 0.4.
-The gain remains significant at \SI{23}{\percent} for a dusty day at $\tau$ factor 1.
-The increase in gain observe for $\tau$ factors greater than 1 are inconsequentially tied to negligible distances.
-At Ismenius cavus, a solar cell coverage area of \SI{2.4}{m^{2}} results in \SI{25}{\percent} and \SI{10}{\percent} gains for $\tau$ factor 0.4 and 1, respectively.
-Applying the same packing efficiency and \ac{SA} surface density as the initial sizing results in \ac{SA} areas of \SI{1.7}{m^{2}} at Iani Chaos with a mass of \SI{6.3}{\kilo\gram} and \SI{2.8}{m^{2}} at Ismenius Cavus with a mass of \SI{10.4}{\kilo\gram}.
-The maximum daily traverse durations attainable at both sites with these target \ac{SA} areas are shown in \refFig{fig:plot:final-maximum-traverse-durations-at-missions-sites}.
-However, these gains come with significantly reduced maximum flat traverse distance coverage of \SI{12}{\kilo\meter} at Iani Chaos and \SI{35}{\kilo\meter} at Ismenius Cavus.
-Mission design with or without \ac{SA} surface inclination thus not only depend on \ac{SA} size and mass constraints but also on mission requirements with respect to target traverse coverages.
-
-\begin{figure}[h]
-\captionsetup[subfigure]{justification=centering}
-  \centering
-  \setlength{\subfigureWidth}{0.24\textwidth}
-  \setlength{\graphicsHeight}{40mm}
-  \begin{subfigure}[t]{\subfigureWidth}
-    \centering
-    \includegraphics[height=\graphicsHeight]{figures/plots/ianichaos-75w-max-traverse-durations-for-solar-cell-coverage-area-15m2.png}
-    \subcaption{Iani Chaos, solar cell coverage = \SI{1.5}{m^{2}}}
-    \label{fig:plot:sub:final-maximum-traverse-durations-iani-chaos}
-  \end{subfigure}\hfill
-  \begin{subfigure}[t]{\subfigureWidth}
-    \centering
-    \includegraphics[height=\graphicsHeight]{figures/plots/ismeniuscavus-75w-max-traverse-durations-for-solar-cell-coverage-area-24m2.png}
-    \subcaption{Ismenius Cavus, solar cell coverage area = \SI{2.4}{m^{2}}}
-    \label{fig:plot:sub:final-maximum-traverse-durations-ismenius-cavus}
-  \end{subfigure}
-  \caption{Maximum traverse durations at mission sites. The same considerations were taken as in \refFig{fig:plot:ismenius-cavus-generated-energy-and-max-traverse-durations}.}
-  \label{fig:plot:final-maximum-traverse-durations-at-missions-sites}
-\end{figure}
-
-\ac{SA} sizing with the hibernation reference Sol power budget defined in \refTab{tab:hibernation-sol-power-budget} as the worst case power budget fails to meet the target \ac{SA} areas.
-However, the required power draws only differ by a few Watts.
-At Iani Chaos, this is achieved by reducing the hibernation mode power draws from \SI{18}{\watt} to \SI{17}{\watt}.
-At Ismenius Cavus, hibernation power draws need to be reduced from \SI{18}{\watt} to \SI{15}{\watt}.
-Taking into account a \SI{20}{\percent} system margin, the energy requirement for hibernation Sols become \SI{490}{\watt\hour} at Iani Chaos for a \SI{1.7}{m^{2}} \ac{SA} area and \SI{432}{\watt\hour} at Ismenius Cavus for a \SI{2.8}{m^{2}} \ac{SA} area.
-\refFig{fig:rover-body-redesign} shows the rover's body redesign from a pyramid to a cubic shape in order to better accommodate the \ac{SA} surface and avoid shadowing.
-
-\begin{figure}[h]
-\captionsetup[subfigure]{justification=centering}
-  \centering
-  \setlength{\subfigureWidth}{0.24\textwidth}
-  \setlength{\graphicsHeight}{29mm}
-  \begin{subfigure}[t]{\subfigureWidth}
-    \centering
-    \includegraphics[height=\graphicsHeight]{figures/images/body-before.png}
-    \subcaption{Before}
-    \label{fig:sub:rover-body-redesign-before}
-    \end{subfigure}\hfill
-  \begin{subfigure}[t]{\subfigureWidth}
-    \centering
-    \includegraphics[height=\graphicsHeight]{figures/images/body-after.png}
-    \subcaption{After}
-    \label{fig:sub:rover-body-redesign-after}
-  \end{subfigure}
-  \caption{Rover body redesign.}
-  \label{fig:rover-body-redesign}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Simulation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The proposed rover and \ac{SA} configurations are modeled with Blender/Phobos and loaded into MARS for mission scenario simulation.
-Phobos is ``an add-on for the open-source 3D modeling software Blender that enables the creation of robot models for use in robot frameworks like ROS and ROCK or in real-time simulations such as MARS'' \cite{Phobos}.
-MARS is ``a cross-platform simulation and visualization tool created for robotics research.
-It consists of a core framework containing all main simulation components, a GUI (based on Qt), 3D visualization (using OSG) and a physics engine (based on ODE)'' \cite{MARSSim}.
-
-\subsection{Z-Axis Revolutions}
-
-\refFig{fig:sub:simulation-data-rover-revolution-generated-power-line-chart} and \refFig{fig:sub:simulation-data-rover-revolution-generated-power-polar-chart} are two different representations of the same solar power output obtained from commanding the rover to execute a \SI{10}{\degree} forward body-pitch followed by several revolutions around its z-axis.
-These revolutions result in a sinusoidal power output variation.
-Local spikes and dips are noted around \SI{100}{\second} and \SI{160}{\second} due to small changes in the \ac{SA} inclination and orientation angles caused by the rover driving over uneven terrain.
-In \refFig{fig:sub:simulation-data-rover-revolution-generated-power-polar-chart}, the angle values represent the direction faced by the inclined \ac{SA}.
-Maximum power is generated when the \ac{SA} is oriented southwards, towards the equator, in the general direction of the sun.
-Inversely, facing northwards, away from the sun, generates the least amount of power.
-These are the expected results thus validating the simulation environment for further development and mission scenario analysis.
-
-\begin{figure}[h]
-  \captionsetup[subfigure]{justification=centering}
-  \centering
-  \setlength{\subfigureWidth}{0.24\textwidth}
-  \setlength{\graphicsHeight}{40mm}
-  \begin{subfigure}[t]{\subfigureWidth}
-    \centering
-    \includegraphics[height=\graphicsHeight]{figures/plots/zaxis-revolutions.png}
-    \subcaption{Line chart}
-    \label{fig:sub:simulation-data-rover-revolution-generated-power-line-chart}
-  \end{subfigure}\hfill
-  \begin{subfigure}[t]{\subfigureWidth}
-    \centering
-    \includegraphics[height=\graphicsHeight]{figures/plots/zaxis-revolutions-polar.png}
-    \subcaption{Polar chart}
-    \label{fig:sub:simulation-data-rover-revolution-generated-power-polar-chart}
-  \end{subfigure}\\[0.6ex]
-  \caption{Power generated by the rover's \ac{SA} for multiple revolutions along its z-axis.
-Simulation condition is solar noon at Ismenius Cavus with $\beta \approx \SI{10}{\degree}$.
-In the polar chart, angle values represent the direction faced by the inclined \ac{SA} where \SI{0}{\degree} is South (towards the equator), \SI{-90}{\degree} is East, \SI{180}{\degree} is North, and \SI{90}{\degree} is West.}
-  \label{fig:simulation-data-rover-revolution-generated-power}
-\end{figure}
-
-\subsection{Slope Compensation}
-
-The worst case slope traverse is on an inclined surface facing away from the sun.
-The rover's active suspension system can be used to reduce the \ac{SA} inclination angle by commanding a rover body pitch in the opposite direction.
-This slope compensation scenario is illustrated in \refFig{fig:sub:rover-on-slope-beta} where $B$ denotes the slope surface inclination angle and $\beta$ the \ac{SA} surface inclination angle.
-
-\begin{figure}[h]
-\captionsetup[subfigure]{justification=centering}
-  \centering
-  \begin{subfigure}[t]{\subfigureWidth}
-    \centering
-    \includegraphics[height=\graphicsHeight]{figures/images/stick-rover-beta-large.png}
-    \subcaption{$\beta = B$}
-    \label{fig:sub:rover-on-slope-beta-large}
-  \end{subfigure}\hfill
-  \begin{subfigure}[t]{\subfigureWidth}
-    \centering
-    \includegraphics[height=\graphicsHeight]{figures/images/stick-rover-beta-small.png}
-    \subcaption{$\beta < B$}
-    \label{fig:sub:rover-on-slope-beta-small}
-  \end{subfigure}
-  \caption{Slope compensation with active suspension system to reduce the \ac{SA} surface inclination angle.
-Slope inclination angle $B = \SI{30}{\degree}$.
-In (a), $\beta = B = \SI{30}{\degree}$.
-In (b), the rover is tilted \SI{10}{\degree} in the opposite direction of the slope so that $\beta = \SI{20}{\degree}$.}
-  \label{fig:sub:rover-on-slope-beta}
-\end{figure}
-
-By way of example, at Ismenius Cavus for a $\tau$ factor of 0.4 and an areocentric longitude $L_{s}$ of \SI{270}{\degree}, descending a \SI{30}{\degree} slope bearing North results in a daily insolation of \SI{319}{Whm^{-2}}.
-This is increased to \SI{767}{Whm^{-2}} by decreasing $\beta$ from \SI{30}{\degree} to \SI{25}{\degree} after tilting the rover southwards by \SI{5}{\degree} so that $\beta < B$.
-A \SI{10}{\degree} tilt would increase the daily insolation to \SI{1046}{Whm^{-2}} with $\beta = \SI{20}{\degree}$.
-The solar power generated from this scenario is simulated.
-\refFig{fig:sub:rover-on-slope-beta} shows solar power outputs for different body-pitch configuration while the rover is on a \SI{30}{\degree} slope.
-The initial state of the \ac{SA} surface inclination angle is equal to that of the slope angle.
-Two separate \SI{5}{\degree} forward pitch increments are executed at \SI{25}{\second} and \SI{35}{\second} which worsen solar power output by changing the \ac{SA} surface inclination angle from $\sim$\SI{30}{\degree} to $\sim$\SI{40}{\degree}.
-Four separate \SI{5}{\degree} backward pitch decrements are executed from \SI{45}{\second} to \SI{65}{\second}, progressively improving power generation as $\beta$ is decreased from $\sim$\SI{40}{\degree} to $\sim$\SI{20}{\degree}.
-As a final task, the rover is commanded to drive forward at \SI{80}{\second} and it encounters uneven terrain which introduces minor fluctuations to the solar power output.
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=3.25in]{figures/plots/slope-compensation.png}
-  \caption{Slope compensation with active suspension system to reduce the \ac{SA} surface inclination angle.
-Slope inclination angle $B = \SI{30}{\degree}$.
-In (a), $\beta = B = \SI{30}{\degree}$.
-In (b), the rover is tilted \SI{10}{\degree} in the opposite direction of the slope so that $\beta = \SI{20}{\degree}$.}
-  \label{fig:sub:rover-on-slope-beta}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The findings of this paper support using the SherpaTT rover active suspension system as a mechanism for solar panel inclination and orientation under certain \ac{SA} sizing conditions.
@@
 In light of this, \ac{SA} sizing for the the worst case daily insolations introduce a hibernation mode solar power draw constraint of \SI{17}{\watt} near the equator at \SI{2}{\degree}S and \SI{15}{\watt} in the northern hemisphere at \SI{34}{\degree}N.
-With these power budgets, an average traverse gain of \SI{34}{\percent} is achieved at \SI{2}{\degree}S for a clear day with a $\tau$ factor of 0.4.
+\comment{With these power budgets, an average traverse gain of \SI{34}{\percent} is achieved at \SI{2}{\degree}S for a clear day with a $\tau$ factor of 0.4.
 At \SI{34}{\degree}N, the average gain is \SI{25}{\percent} under the same atmospheric opacity.
-These gains remain significant on dusty days at \SI{23}{\percent} and \SI{10}{\percent} at respective latitudes with a $\tau$ factor of 1.
+These gains remain significant on dusty days at \SI{23}{\percent} and \SI{10}{\percent} at respective latitudes with a $\tau$ factor of 1.}
 
